Peridynamic Beams: \\ A Non-ordinary, State Based Model

### 2014-02-05 BeamPaper.tex
more edits to Eringen section

We can picture a bending resistance based on the nonlocal curvature  \(\bar{\kappa}\), so that 

@@

\alpha\bar{\kappa}&= \alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies \notag \\

@@

Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus (denoted here as \(K(|\mathbf{x}'-\mathbf{x}|,\tau)\)) that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material through the integral
\begin{equation}
\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
\end{equation}
In the local limit these relationships take the form of higher-order gradients.
Using a decaying exponential nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
\begin{align}
\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
\end{align}
in which \(\tau^2l^2\) is a scale-based material parameter.
For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
\begin{equation}
\mathbf{t}=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\boldsymbol{\sigma}.\notag
\end{equation}

%This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
The similarity is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.

>>>>

We can picture a bending resistance based on the bond length and the nonlocal curvature  \(\bar{\kappa}\), so that 

@@

\label{eq:NLbending}
 \omega(\xi)\alpha\bar{\kappa}&=  \omega(\xi)\alpha(\kappa + \frac{\xi^2}{6}\kappa'') \implies  \\

@@

Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus (denoted here as \(K(|\mathbf{x}'-\mathbf{x}|,\tau)\)) that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material through the integral
\begin{equation}
\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
\end{equation}
In the local limit these relationships take the form of higher-order gradients.
Using a 1-dimensional decaying exponential nonlocal modulus \(K(|x|,\tau)=\frac{1}{l\tau}e^{-\frac{|x|}{l\tau}}\)results in a relationship between \(t\) and \(\sigma\) 
\begin{align}
\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)t&=\sigma,\notag
\end{align}
in which \(\tau^2l^2\) is a scale-based material parameter.
For well-behaved \(t\) and \(\sigma\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
\begin{equation}
\label{eq:NLstress}
t=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\sigma.\notag
\end{equation}
If we consider the results of the previous section and let \(dM = y\sigma dA\) and \(\sigma = Ey\kappa\), the contribution to moment resulting from Eringen's nonlocal elasticity in a fiber at \(y\)
\begin{equation}
\label{eq:EringenMoment}
E y^2 (\kappa+\tau^2l^2\kappa''), \\
\end{equation}
and the resulting strain energy
\begin{equation}
\label{eq:EringenEnergy}
\int_{-\frac{t}{2}}^{\frac{t}{2}} b(y) E \frac{y^2}{2} \kappa (\kappa+\tau^2l^2\kappa'')  dy,\notag
\end{equation}
bear a striking resemblance to \cref{eq:NLbending}.

%This is consistent with Eringen's observation of nonlocal modulus as Green's function of a linear differential operator in~\cite{eringen1983differential}. 
The similarity between \cref{eq:NLbending,eq:EringenMoment} is not accidental; Eringen's gradient elasticity is the solution to the integral formulation of the nonlocal stress integral equation just as the peridynamic energy is an integral function of nonlocal displacements.
